%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv} % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
% moderncv themes
\moderncvstyle{classic} % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault} % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{} % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc} % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8} % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean
\usepackage[resetlabels,labeled]{multibib}
% adjust the page margins
\usepackage[scale=0.77]{geometry}
%\setlength{\hintscolumnwidth}{3cm} % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm} % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
% personal data
\name{Reza}{Monadi}
% \title{Objective: Carnegie/UC Riverside fellowship} % optional, remove / comment the line if not wanted
% \address{950 W Linden St.}{92507 Riverside}{USA}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
% \phone[mobile]{+1~(951)~396~6497} % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901} % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012} % optional, remove / comment the line if not wanted
% \email{reza.monadi@email.UC Riverside.edu} % optional, remove / comment the line if not wanted
% \homepage{Google Scholar}{https://scholar.google.com/citations?user=X2WtEvoAAAAJ&hl=en} % optional, remove / comment the line if not wanted
% \extrainfo{University of California, Riverside} % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture} % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote} % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
% content
 
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn} % to typeset your resume in Chinese using CJK
%----- resume ---------------------------------------------------------newpage
\section{Reza Monadi}
\cvitem{Address}{University of California Riverside, Physics and Astronomy Department,   
    900 University Ave., Riverside, CA 92521 }
\cvitem{Email}{reza.monadi@email.UC Riverside.edu}
\cvitem{Phone}{+1 (951) 396-6497}
\cvitem{Website}{https://rezamonadi.github.io/}
\cvitem{Linkedin}{https://www.linkedin.com/in/reza-monadi}



\section{Education}
\cventry{Ph.D.}{Physics, University of California, Riverside}{California}{USA}{2017-2023}{Thesis Topic: Statistical studies 
of quasar spectra}
\cventry{M.Sc.}{Astrophysics, Shahid Beheshti University}{Tehran}{Iran}{2010-2013}{Thesis Topic:
Statistical studies of glitches in pulsars}
\cventry{B.Sc.}{Physics, University of Guilan}{Rasht}{Iran}{2005-2009}{}

% \newpage
\section{Teaching Experience}
\cventry{Winter 2024}{Lecturer}{Cal Poly SLO }{San Luis Obispo }{Physics 143 (Calc-based E\&M)}{I}
\cventry{Winter 2024}{Lecturer}{Cal Poly SLO }{San Luis Obispo }{Astronomy 101 (Intro to Solar Sytem)}{I}
\cventry{Fall 2023}{Lecturer}{Cal Poly SLO }{San Luis Obispo }{Physics 143 (Calc-based E\&M)}{I}
\cventry{Spring 2022}{Teaching Assistant}{Discussion: Electricity and Magnetism}{UC Riverside}{I helped the students to work out the problems in their assigned groups.  
Then I directed group heads to discuss their solutions with the rest of the class.}{}
\cventry{Fall 2021 and winter 2022}{Teaching Assistant}{Discussion: Physics for life sciences}{UC Riverside}{I discussed some problems in each session while asking for volunteers to express their ideas about each question.}{}
\cventry{}{Teaching Assistant}{Discussion: Adventure in astronomy and astrophysics}{UC Riverside}{Spring 2021}{We discussed some problems in each session and then I gave a relevant quiz to the class.}{}
\cventry{}{Teaching Assistant}{Discussion: Space-Time, Relativity, And Cosmology}{UC Riverside}{Winter 2021}{I reviewed the instructor's main points and then took a quiz at the end.}{}
\cventry{}{Teaching Assistant}{Lab: General Physics}{UC Riverside}{Winter 2019}{I gave a short lecture at the beginning, give a pre-quiz, helped students with any issues with their lab manual or pieces of equipment, and graded their lab reports.}{}
\cventry{}{Teaching Assistant}{Lab: Electricity and Magnetism}{UC Riverside}{Fall-2017, Winter-2018}{I wrote pre-lab quizzes and helped students in understanding the lab manual and electrical circuits and equipment. Also, I graded their lab report}{}
\cventry{}{Teaching Assistant}{Lab: Electricity and Magnetism}{University of Guilan}{2015-2017}{I wrote exams, prepared lectures, helped them in performing experiments, and graded their reports and exams.}{}
\cventry{}{Teacher}{Astronomy}{Mirza Kouchak High School}{2015-2017}{I thought introductory astronomy, conducted some research projects about 
physics and astronomy, helped them in a science fair competition, and I was a judge in a student research competition.}{}
\cventry{}{Teacher}{Astronomy and Cosmology}{Thaqib Astronomical Association}{2012-2017}{I thought cosmology and introductory astronomy in various classes during the summer program of the astronomy association.}{}
\section{Research Experience}
    \cvlistitem{\textbf{Selecting Extremely Red Quasars using Machine Learning:\\}
     I carried out different \emph{clustering analyses} and \emph{outlier detection} methods and did a 
     comparative analysis on the spectra of extremely red quasars. We could find more exotic quasars in the class
     of extremely red quasars in a  large sample of more than 30000 objects which was very challenging. Our machine learning-based selection criteria could find more extremely red quasars with even more exotic physical properties.    }
    \cvlistitem{\textbf{Catalogging CIV absorption lines using machine learning:\\}
    I built the largest triply ionized carbon absorption catalog using 
    \emph{machine learning} which is combination of \emph{Bayesian} analysis and \emph{Gaussian Processes}.
    I classified a large sample of quasars (Sloan Digital Sky Server DR12) consisting of more than 185000 objects. The 
    resultant catalog will be widely used by our group and other astrophysicists and will have a lot of
    impact on the community.  I presented a poster and gave a short talk at a conference about this project. Also, I am preparing a paper.}
    

% \cvlistitem{\textbf{Data mining graduate  course research}: 
%     \textit{ I did \textbf{outlier detection} and \textbf{dimensionality reduction} to uncover a population of 
%     outlier Quasars in SDSS DR16Q and \textbf{visualize} them. I got an $A^{+}$ in this course considering that 
%     it was offered to graduate students in a different department (i.e. department of computer sciences).}}
    \cvlistitem{\textbf{Statistical study of glitch in pulsars:\\}
     I did \textbf{correlation analysis} and \textbf{statistical inference} to study glitches in radio 
    pulsars. I investigated if the glitch events are random or can be modelled 
    by  Poisson processes. This resulted in my master's dissertation. }
    \cvlistitem{\textbf{General Relativity of charged and magnetized super dense stars:\\ } 
    We studied the stellar structure of a charged and magnetized strange quark star. 
    We made a novel assumption about the internal pressure of strange quark stars and our 
    calculations were compatible with a newly observed mass of a pulsar which could not be explained by previous models.
    This project resulted in a paper published in the Chinese Physics Letters journal.}
    \cvlistitem{\textbf{Complexity of pulsars pulse profile:\\}
    We used complexity measures in the literature and introduced a novel one and then examined them 
    on a sample of high-resolution millisecond pulsars pulse profiles. Then we simulated some pulse profiles 
    and tested our algorithm on them. We then try to relate the complexity of a pulsar pulse profile.
    to the physical properties of pulsars. We submitted a paper about this project to the Monthly Notices of Royal Astronomy journal and it is under review.}
    % \cvlistitem{\textbf{Undergraduate research:} 
    % \textit{I designed and built a simple but novel solar positioning system. I presented 
    % my project as a poster at the most important annual physics conference in Iran considering most of 
    % the participant were graduate students while I was an undergrad. }}
% \newpage

\section{Publications}
\cvlistitem{Studying Carbon in quasar absorption lines: Constructing the catalog with Gaussian processes, 
\textbf{Reza Monadi}, Simeon Bird, Ming-Feng Ho, Kathy Cooksey (in prep.)}
\cvlistitem{Pulse Profile Complexity of Millisecond Pulsars, \\ I. Eghdami, \textbf{R. Monadi}, SMS Movahed, H. Panahi, (Submitted to Monthly Notices of the Royal Astronomical Society)}
\cvlistitem{Improved selection of extremely red quasars with boxy CIV lines in BOSS, \textbf{R. Monadi}, Simeon Bird, Monthly Notices of the Royal Astronomical Society 511 (3), 3501-3513}
\cvlistitem{A Gaussian Model for Anisotropic Strange Quark Stars:
H. Panahi, \textbf{R. Monadi} and I. Eghdami, Chinese Physics Letters 33 (7), 072601, 2016,} 
\newpage
\section{Presentation}
\cvlistitem{\textbf{Talk + Poster:} Detecting CIV absorption lines in SDSS spectra with Gaussian Processes\\
 Debating the potential of machine learning in astronomical surveys,  Institut d'Astrophysque de Paris, France, 2021}
\cvlistitem{\textbf{Poster:} Improved selection of extremely red quasars with boxy CIV lines\\
Statistical Challenges in Modern Astronomy VII, Pennsylvania University, USA, 2021}
\cvlistitem{\textbf{Talk + Poster:} Precise Selection of Extremely Red Quasars\\
Keck Science Meeting, University of California, Los Angeles, USA, 2019}
% \newpage
% \section{Research Skills}
% % \cventry{Problem solving}{Finding simple solutions for complex problems.}{}{}{}{}
% \cventry{Programming languages}{Python, MATLAB, FORTRAN, SQL}{}{}{}{}
% \cventry{High-Performance Computing}{UC Riverside's HPC cluster, Amazon Web Service}{}{}{}{}
% % \cventry{}{ Scipy, Matplotlib, Scikit-learn, PyClustering}{}{}{}{}
% \cventry{Machine Learning}{Outliers, Clustering, Classification, Dimensionality reduction,... }{}{}{}{}
% \cventry{Statistics }{Bayesian Analysis, Gaussian Processes, ...}{}{}{}{}


\section{Services}
\cventry{Helper}{2021 Fall Joint UC Software Carpentry Workshops}{Helping in the Unix Shell workshop}{}{2021}{}{}
\cventry{Assistant Rviewer}{Journal of Cosmology and Astroparticle Physics}{Feb. 2022}{}{}{}
\cventry{Educator}{Cosmic Thursdays}{Teaching K-12 students about StellarEvolution}{UC Riverside}{2021}{}{}
\cventry{Organizing assistant}{Cosmic Thursdays}{}{UC Riverside}{2019}{}{}
\cventry{Scientific Judge}{Riverside County Science and Engineering Fair}{Riverside Convention Center}{2019}{}{}
\cventry{Educator}{Apollo Event}{Performing hands-on activities}{UC Riverside}{2019}{}{}
\cventry{Scientific Judge}{MESA 2018}{High school student competition}{UC Riverside}{2019}{}{}
\cventry{Scientific Organizer}{Science Fair}{Thaqib Astronomy Association}{Iran}{2017}{}
\cventry{Educator}{Astronomy public club}{Giving astronomy talks at Thaqib astronomy association}{Iran}{2013-2017}{}{}
% \newpage
\section{Honours and Awards}
\cvlistitem{Travel grant for giving a talk in the \emph{"Statistical Methods for Event Data
Illuminating the Dynamic Universe"} conference from the conference organizers.}
\cvlistitem{UC Riverside's graduate students association travel grant for attending two confrences}
\cvlistitem{Dean's distinguished fellowship award, UC Riverside, 2017-2020}
\cvlistitem{Top 2$\%$ in PhD program applicants for physics in Iran, 2013}
\cvlistitem{Top 1$\%$ in MSc program applicants for physics in Iran, 2010}
\section{Membership}
\cvlistitem{International Astrostatistics Association, since Feb. 2020}
\cvlistitem{Riverside Astronomical Society, since 2022}
\newpage
\section{Reference}
\cvlistitem{\textbf{Simeon Bird}: Assistant professor\\Department of physics and astronomy at University of California Riverside\\Email: sbird@UC Riverside.edu}
\cvlistitem{\textbf{Evangelos Papalexakis:}  Associate professor\\Department of computer sciences at University of California Riverside\\Email:epapalexcs@cs.UC Riverside.edu}
\cvlistitem{\textbf{Jose Wudka:} Divisional Dean Physical Sciences and Mathematics\\Department of Physics and astronomy at University of California Riverside\\Email: jose.wudka@ucr.edu }
\cvlistitem{\textbf{Dr. Seyed Mohammad Sadegh Movahed:} Full Professor\\Department of physics at Shahid Beheshti University, Tehran, Iran \\Email: m.s.movahed@ipm }
% audiences 
\end{document}
 

