\documentclass[11pt,letterpaper]{scrartcl}

% ---------- Packages ----------
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{mathpazo}      % Palatino text/math for readability
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{parskip}       % No paragraph indents; adds vertical space

% ---------- Look & feel ----------
\definecolor{accent}{HTML}{1A4A7A} % deep blue (prints well in B/W)
\setlist[itemize]{left=0pt..1.3em,itemsep=3pt,topsep=3pt}
\setlist[enumerate]{leftmargin=1.6em,itemsep=4pt,topsep=4pt}
\setlength{\tabcolsep}{4pt}
\renewcommand{\labelitemi}{\textbullet}
\pagestyle{empty}

\newcommand{\Name}{Reza Monadi}
\newcommand{\Email}{rmonadi@calpoly.edu}
\newcommand{\Phone}{805--756--0679}
\newcommand{\Dept}{Department of Physics}
\newcommand{\Inst}{California Polytechnic State University, San Luis Obispo }
\newcommand{\Addr}{1 Grand Ave, San Luis Obispo, CA 93407}

% Section header with rule
\newcommand{\cvsection}[1]{%
  \vspace{4pt}%
  {\large\bfseries\textcolor{accent}{#1}}\par
  \vspace{2pt}\hrule\vspace{6pt}
}

% Entry helpers
\newcommand{\entry}[3]{% role/institution — right-aligned date
  \noindent\textbf{#1}\quad #2 \hfill {\small #3}\par
}
\newcommand{\subentry}[2]{% course/title — right-aligned terms
  \noindent #1 \hfill {\small #2}\par
}

\begin{document}

% ---------- Header ----------
\begin{minipage}[t]{0.64\textwidth}
  {\LARGE\bfseries \Name}\par
  \vspace{2pt}
  \Dept, \Inst \\
  \Addr
\end{minipage}%
\hfill
\begin{minipage}[t]{0.33\textwidth}\raggedleft
  \href{mailto:\Email}{\Email}\\
  \Phone
\end{minipage}

\vspace{6pt}\hrule\vspace{10pt}

% ---------- Interests ----------
\cvsection{Research Interests}
\begin{itemize}
\item{Quasar absorption lines (C~IV, Mg~II)}
\item Intergalactic/CGM physics
\item Machine learning and Bayesian inference
\item Large spectroscopic surveys (SDSS/BOSS/DESI)
\end{itemize}

\cvsection{Teaching Interests}
\begin{itemize}
\item Introductory and upper-division courses in physics and astronomy
\item Computational physics and scientific programming
\item Data analysis and statistics for physicists
\item Observational astronomy and astrophysics
\end{itemize}

% ---------- Education ----------
\cvsection{Education}
\entry{University of California, Riverside}{Ph.D., Physics}{Aug 2023}
\emph{Dissertation:} Statistical Studies of Quasar Spectra \\
\emph{Advisor:} Simeon Bird

\entry{University of California, Riverside}{M.Sc., Physics}{Mar 2023}

\entry{Shahid Beheshti University, Tehran, Iran}{M.Sc., Astrophysics}{2013}
\emph{Thesis:} Statistical Studies of Glitches in Pulsars

\entry{University of Guilan, Rasht, Iran}{B.Sc., Physics}{2009}

% ---------- Appointments ----------
\cvsection{Academic Appointments}
\entry{Lecturer}{\Dept, \Inst}{Sep 2023--present}

% ---------- Teaching ----------
\cvsection{Teaching Experience }
\textbf{Lecturer (Cal Poly)}\par
\subentry{\textbf{PHYS 141} (General Physics I)}{Fall 2025}
\subentry{\textbf{PHYS 122 Lab}}{Fall 2025}
\subentry{\textbf{PHYS 143} (General Physics III)}{Fall 2023; Winter 2024; Spring 2024; Spring 2025}
\subentry{\textbf{PHYS 142 Lab} (General Physics II Lab)}{Winter 2025}
\subentry{\textbf{PHYS 121} (College Physics I)}{Fall 2024}
\subentry{\textbf{ASTRO 101} (Introductory Astronomy)}{Winter 2024; Spring 2024; Summer 2024; Fall 2024; Winter 2025}
\subentry{\textbf{ASTRO 102}}{Summer 2024}

\textbf{Teaching Assistant (UC Riverside)}\par
\subentry{PHYS 40C (Electricity \& Magnetism)}{Spring 2022; Fall 2017; Winter 2018}
\subentry{PHYS 2LB (Physics for Life Sciences Lab)}{Fall 2021; Winter 2022}
\subentry{PHYS 20 (Adventures in Astronomy \& Astrophysics)}{Spring 2021}
\subentry{PHYS 7 (Space-Time, Relativity \& Cosmology)}{Winter 2021}

% ---------- Advising ----------
\cvsection{Advising \& Mentoring}
\subentry{Research Advisor, Frost Summer Research, four undergraduates, Cal Poly}{Summer 2024 and 2025}
\subentry{Senior Project Advisor, three undergraduates, Cal Poly}{(Winter 2025--present) }
\subentry{REU Advisor, one undergraduate, UC Riverside }{Summer 2023 }
\subentry{Senior Project Advisor, University of Guilan (Iran)}{Summer 2017}

% ---------- Publications ----------
\cvsection{Publications (peer-reviewed)}
\begin{enumerate}[label=\arabic*.,leftmargin=1.6em]
  \item \textbf{Monadi, R.}, Ho, M.-F., Cooksey, K., Bird, S. (2023).
  Machine learning uncovers the Universe’s hidden gems: A comprehensive catalogue of C~IV absorption lines in SDSS DR12.
  \emph{Monthly Notices of the Royal Astronomical Society}, 526(3), Dec 2023. [Lead author]

  \item Bird, S., Fernandez, M., Ho, M.-F., Qezlou, M., \textbf{Monadi, R.}, Ni, Y., Chen, N., Croft, R., Di~Matteo, T. (2023).
  PRIYA: A new suite of Lyman-\texorpdfstring{$\alpha$}{alpha} forest simulations for cosmology.
  \emph{Journal of Cosmology and Astroparticle Physics}, Oct 2023.

  \item \textbf{Monadi, R.}, Bird, S. (2022).
  Improved selection of extremely red quasars with boxy C~IV lines in BOSS.
  \emph{Monthly Notices of the Royal Astronomical Society}, 511(3), 3501--3513. [Lead author]

  \item Panahi, H., \textbf{Monadi, R.}, Eghdami, I. (2016).
  A Gaussian model for anisotropic strange quark stars.
  \emph{Chinese Physics Letters}, 33(7), 072601.
\end{enumerate}

% ---------- Presentations ----------
\cvsection{Conference Presentations \& Talks}
\textbf{American Astronomical Society 245}, National Harbor, MD, Jan 12--16, 2025 — Undergraduate posters (advisor): \\
\quad Detecting C~IV Absorbers Through Gaussian Processes and Bayesian Analysis (Wilson-Goodwin*, Hughes, \textbf{Monadi}) \\
\quad Detecting Mg~II Absorbers in the Intergalactic Medium Using SDSS DR7 Quasar Catalog (Hughes*, Wilson-Goodwin, \textbf{Monadi}) \\[4pt]
\textbf{N3AS Workshop}, UC Santa Cruz, Summer 2023 — Talk: Metal lines catalog for the intergalactic medium \\
\textbf{AAS 242}, Albuquerque, NM, Jun 2023 — Talk: Machine learning uncovers the hidden gems of the Universe \\
\textbf{IID 2022 Conference}, Alabama, Nov 2022 — Talk: Cataloging metal lines using machine learning \\
\textbf{Debating the Potential of Machine Learning in Astronomical Surveys}, Institut d’Astrophysique de Paris, 2021 — Talk: Detecting C~IV absorption lines in SDSS spectra with Gaussian Processes \\
\textbf{Statistical Challenges in Modern Astronomy VII}, Penn State, 2021 — Poster: Improved selection of extremely red quasars with boxy C~IV lines \\
\textbf{Keck Science Meeting}, UCLA, 2019 — Talk + Poster: Precise selection of extremely red quasars

% ---------- Grants ----------
\cvsection{Grants \& Internal Funding}
Frost Fund, \textbf{PI}, \$1{,}000 — Fall 2023. AWS computing credits for quasar absorption research (used by Jun 2024). \\
Frost Fund, \textbf{PI}, \$2{,}800 — Winter 2024. Desktop workstation for undergraduate researchers (used by Jun 2024). \\
Instructionally Related Activity (IRA) Fund, \textbf{PI}, \$750 — Spring 2025. Raspberry Pi and radio-telescope antenna for astronomy teaching; acquired two educational radio telescopes.

% ---------- (Optional) Skills / Service ----------
\cvsection{Service \& Outreach}
\subentry{Astronomy Commitee Memeber}{2023--present}
\subentry{Cal-Bridge Mentor}{Sep. 2025--present}

\cvsection{Refrences}
\subentry{\textbf{Simeon Bird}, Associate Professor, UC Riverside \\
\textbf{Email:} sbird@ucr.edu\\
\textbf{Phone:} 951--827--5108 \\}

\subentry{\textbf{Matt Molter}, Professor, Cal Poly \\
\textbf{Email:} mmoelter@calpoly.edu\\
\textbf{Phone:} 805--756--2656}

\subentry{\textbf{ Robert Echols}, Professor, Cal Poly \\
\textbf{Email:} rechols@calpoly.edu\\
\textbf{Phone:} 805--756--7649}

\end{document}
